\Title

### 2021-02-16 manuscript/content.tex
Specify symbol of residuals on caption
Change location of figure and adequate text to it

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (Fig.~\ref{fig:gradient-boosting-schematics}b).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosting algorithm.
        Given a set of data points (blue upwards triangles), define a set of
        equivalent sources (orange dots).
        Start the gradient-boosting algorithm by selecting the data points and
        the sources that fall under one of the overlapping windows, and
        estimate their coefficients by fitting against this portion of the
        data.
        Then predict the effect of this set of sources on every observation
        point and calculate the residuals.
        Use another window to select residual points and sources that fall
        under it, and estimate their coefficients by fitting them against the
        selected residual points.
        Predict the effect of this set of sources on every observation point
        and update the residue.
        Repeat this step for every remaining window.
        The order in which the windows are covered is randomized to improve
        convergence of the algorithm.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}

@@

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (Eq.~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient-boosted equivalent source algorithm}.

@@

>>>>

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area.
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

@@

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit} of
algorithm~\ref{alg:gradient_boosting}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
of algorithm~\ref{alg:gradient_boosting}).
By doing so, we can reduce the size of the Jacobian matrix further to $N_k
\times M_k$ elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (Eq.~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
the final \textit{gradient-boosted equivalent source algorithm}.
Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the
gradient-boosted equivalent source algorithm with a set of observation points
that simulate a ground survey and locating one source below each data point.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosted equivalent source algorithm.
        Given a set of data points (blue upwards triangles), define a set of
        equivalent sources (orange dots) by locating one source below each
        observation point.
        Start the gradient-boosting algorithm by selecting the data points and
        the sources that fall under one of the overlapping windows, and
        estimate their coefficients by fitting against this portion of the
        data.
        Then predict the effect of this set of sources on every observation
        point and calculate the residuals (red downward triangles).
        Use another window to select residual points and sources that fall
        under it, and estimate their coefficients by fitting them against the
        selected residual points.
        Predict the effect of this set of sources on every observation point
        and update the residuals.
        Repeat this step for every remaining window.
        The order in which the windows are covered is randomized to improve
        convergence of the algorithm.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}
